Maximum Allowable Current Determination of RBS By Using a Directed Graph Model and Greedy Algorithm

### 2023-11-09 paper/SST/3-response_reviewer1.tex

% Reviewer 1
\reviewer
% Comment 1
\begin{revcomment}
  Grammatical and spelling errors are still observed. Please check and fix carefully.
\end{revcomment}
\begin{revresponse}

We are sorry for our negligence of the grammatical and spelling errors, and have carefully checked the manuscript and corrected them.

\end{revresponse}

% Comment 2
\begin{revcomment}
  Since authors stated that there is no existing works on the MAC determination of RBSs that they could compare their solution with. So how the authors validate their works and their results.
\end{revcomment}
\begin{revresponse}

We infer that the reviewer may desire to convey: since the authors stated that there are no existing works on the MAC determination of RBSs that they could compare their solution with, it is important to meticulously and comprehensively elucidate how the authors validate their works and the results.

To address the concern raised by the reviewer, we have incorporated a comprehensive discussion in the Case study section, specifically titled "Correctness of the results". 
In this part, we thoroughly examine the correctness of the results obtained through the proposed greedy algorithm from two distinct perspectives: circuit analysis and validation against the brute-force algorithm. 
Additionally, we have included a comparison between the proposed greedy algorithm and two heuristic algorithms, namely simulated annealing and genetic algorithm, in the revised manuscript. 
There is a reference ([35] in the manuscript) claiming that the path selection problem under consideration may be NP-hard.
Therefore, it is reasonable to compare the performance of the proposed greedy algorithm with these heuristic approaches, which are commonly employed to tackle NP-hard problems.
Remarkably, our results demonstrate that the proposed greedy algorithm consistently achieves the same or superior outcomes compared to the heuristic algorithms.

Here is the specific modification we made in the Discussion:
\begin{changes}
  \ExecuteMetaData[3-main]{reviewer1-comment2}
\end{changes}
And here is the comparison between the proposed greedy algorithm and the heuristic algorithms in the "Result":
\begin{changes}
  \ExecuteMetaData[3-main]{reviewer1-comment2a}
  \ExecuteMetaData[3-main]{reviewer1-comment2b}
\end{changes}

\end{revresponse}

% Comment 3
\begin{revcomment}
  Refer to the mentioned article as previously stated in comment 8 of the first revision.
\end{revcomment}
\begin{revresponse}

We have reconsidered and modified the corresponding content about the analysis on MAC problem in the introduction. 
The mentioned article becomes important to this paper, therefore, we have cited it in the introduction and accept the reviewer's suggestion.

We have reevaluated and revised the relevant content regarding the analysis of the MAC problem in the introduction. The mentioned article holds significance in this paper, hence we have referenced it in the introduction and acknowledged the suggestion made by the reviewer.

Here is the specific modification we made in the introduction:
\begin{changes}
  \ExecuteMetaData[3-main]{reviewer1-comment3}
\end{changes}

\end{revresponse}

### 2023-11-09 paper/SST/3-response_reviewer2.tex

% Reviewer 2
\reviewer
% Comment 1
\begin{revcomment}
  The latest related works need to be reviewed carlfully please, expecicially the works published in recent year 2022,2023.
\end{revcomment}
\begin{revresponse}

We concur with the reviewer's assertion that it is important for our paper to undergo a thorough review of the most recent relevant literature. 
We have carefully scrutinized the pertinent works from the past five years and made appropriate revisions to the manuscript.
In the "Introduction" section, we provide an overview of the challenges posed by the complex RBS structures in hardware design. 
Furthermore, the estimation and control of the system state of RBSs have been receiving increasing attention in recent time.
Consequently, we have chosen several corresponding methodologies aimed at optimizing the system's performance.

Here is the specific modification in the introduction:
\begin{changes}
  \ExecuteMetaData[3-main]{reviewer2-comment1}
\end{changes}

\end{revresponse}

% Comment 2
\begin{revcomment}
  The greedy algorithm and the brute force algorithm are compared in this paper, but the advantages and disadvantages of this algorithm compared with other algorithms cannot be determined.
\end{revcomment}
\begin{revresponse}

Thanks to the suggestion of the reviewer! 
We have revised the "Discussion" subsection and included a specific part to analyze the advantages and disadvantages of the proposed greedy algorithm in comparison to other algorithms. 
Based on our discussion and comparison, the proposed greedy algorithm demonstrates a significant advantage in terms of its effectiveness and efficiency.
It is also capable of handling RBSs with diverse structures. 
However, this algorithm may encounter challenges when dealing with large-scale problems due to its exponential time complexity.
Furthermore, the simplification of the derivation by assuming that all batteries are identical may introduce a slight bias to the MAC due to variations in open-circuit voltage $u_b$ and internal resistance $r_b$ in reality.
We have also provided a solution to address this issue.

The relevant content has been added to the "Advantages and disadvantages of our method" part within the "Discussion" subsection. 
Once again, we appreciate this constructive comment from the reviewer.

\end{revresponse}

% Comment 3
\begin{revcomment}
  This paper mainly applies to the four-battery system, but the usability of other structures of RBS should also be discussed.
\end{revcomment}
\begin{revresponse}

Thanks for the valuable feedback. 
We have thoroughly considered the comment made by the reviewer.
In response, we have supplemented the case study with a series of experiments on RBSs with variant batteries. 
Overall, the proposed greedy algorithm has been applied to RBSs with three different structures, variant batteries, and scenarios involving random isolated batteries. 
The correctness and efficiency of the proposed greedy algorithm have been verified through the comparison with other algorithms.

The relevant content has been added to the "Case study" section. 
We hope it can address the reviewer's concerns.

\end{revresponse}

### 2023-11-10 paper/SST/3-response_reviewer1.tex

\end{revresponse}

% Comment 2
\begin{revcomment}
  Since authors stated that there is no existing works on the MAC determination of RBSs that they could compare their solution with. So how the authors validate their works and their results.
\end{revcomment}
\begin{revresponse}

We infer that the reviewer may desire to convey: since the authors stated that there are no existing works on the MAC determination of RBSs that they could compare their solution with, it is important to meticulously and comprehensively elucidate how the authors validate their works and the results.

To address the concern raised by the reviewer, we have incorporated a comprehensive discussion in the Case study section, specifically titled "Correctness of the results". 
In this part, we thoroughly examine the correctness of the results obtained through the proposed greedy algorithm from two distinct perspectives: circuit analysis and validation against the brute-force algorithm. 
Additionally, we have included a comparison between the proposed greedy algorithm and two heuristic algorithms, namely simulated annealing and genetic algorithm, in the revised manuscript. 
There is a reference (No. 35 in the manuscript) claiming that the path selection problem under consideration may be NP-hard.
Therefore, it is reasonable to compare the performance of the proposed greedy algorithm with these heuristic approaches, which are commonly employed to tackle NP-hard problems.
Remarkably, our results demonstrate that the proposed greedy algorithm consistently achieves the same or superior outcomes compared to the heuristic algorithms.

Here is the specific modification we made in the "Discussion":
\begin{changes}
  \ExecuteMetaData[3-main]{reviewer1-comment2}
\end{changes}
And here is one of the comparisons between the proposed greedy algorithm and the heuristic algorithms in the "Result" section:
\begin{changes}
  \ExecuteMetaData[3-main]{reviewer1-comment2a}
\end{changes}
For more information on the other compared results and details, please refer to the revised "Case Study" section.

We hope that the reviewer is satisfied with the modifications made to the manuscript.
\end{revresponse}

### 2023-11-10 paper/SST/3-cover_letter.tex
fix and modify cover letter and response

We have thoroughly examined the reviewers' comments and have made revisions, which are indicated in red within the paper. We have made every effort to address the comments and improve our manuscript accordingly. Please find attached the revised version, which we kindly request you to consider.

>>>>

We have thoroughly examined the reviewers' comments and have made revisions, which are indicated in red and blue within the paper. Please find attached the revised version, which we kindly request you to consider.
